\documentclass[11pt,a4paper]{article}
\usepackage{coverletter}

\begin{document}

\CLHeaderMinimal
  {Ivan Ogasawara}
  {}
  {\href{mailto:me@ivanogasawara.com}{me@ivanogasawara.com} · +591 69757089 · \href{https://www.linkedin.com/in/ivan-ogasawara/}{linkedin.com/in/ivan-ogasawara}}

\CLRecipient
  {Hiring Committee — GESIS - Leibniz Institute for the Social Sciences}
  {Köln, Germany}
  {\today}

\CLSubject{Application: Research Associate — Trusted Research Environments \& Researcher Training (DSS-23)}

Dear Hiring Committee,


I'm applying for the "Research Associate in Trusted Research Environments \& Researcher Training (DSS-23)" role.
I combine hands-on software engineering with teaching: \textbf{Research Software Engineer}, \textbf{Technical Lead}, and active \textbf{Instructor/Mentor}.
My work focuses on building libraries, tools, and infrastructure that support research and data projects, with reproducible, and collaborative practices.

I serve as a \textbf{Teaching Assistant} in WorldQuant University's \emph{Applied Data Science Lab} and at \textbf{The GRAPH Courses}, where
I'm \textbf{Instructor} for "Python Basics \& Beyond: Intro to Data Analysis with Python" and \textbf{Teaching Assistant} for
"Generative AI for Work \& Research". I lead workshops and code reviews, mentor projects, and help participants develop clear
habits across areas such as health care, literature review, compilers, DevOps, and AI.

As an engineer, I build and operate backend/data services and CI/CD workflows (Python/Django, Apache Superset, Apache Airflow, REST APIs, containers, packaging).
In public-health RSE roles, I helped deliver epidemiological portals (influenza/dengue).

I am the \textbf{Founder \& Executive Director (free time)} of \textbf{Open Science Labs},
mentoring contributors through internships and \textbf{Google Summer of Code}.
I served as an \textbf{Advisor} at \textbf{pyOpenSci} and on the \textbf{Steering Committee} of the Open Science Framework - Open Source Community.

I can offer GESIS: reproducible platform practices (packaging, CI/CD, documentation),
effective training and mentoring, and open-source leadership aligned with trusted research environments.

Thank you for your consideration.

\CLSignoff{Sincerely}{Ivan Ogasawara}{}

\end{document}
