%% start of file `template.tex'.
%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,a4paper,sans]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% moderncv themes
\moderncvstyle{casual}                             % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue}                               % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

% adjust the page margins
\usepackage[scale=0.75]{geometry}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

% personal data
\name{Ivan}{Ogassavara}
\title{Cientista de Datos}                               % optional, remove / comment the line if not wanted
% \address{street and number}{postcode city}{country}% optional, remove / comment the line if not wanted; the "postcode city" and and "country" arguments can be omitted or provided empty
%\phone[mobile]{+1~(234)~567~890}                   % optional, remove / comment the line if not wanted
%\phone[fixed]{+2~(345)~678~901}                    % optional, remove / comment the line if not wanted
%\phone[fax]{+3~(456)~789~012}                      % optional, remove / comment the line if not wanted
\email{ivan.ogasawara@gmail.com}                               % optional, remove / comment the line if not wanted
\homepage{https://github.com/xmnlab/}                         % optional, remove / comment the line if not wanted
\extrainfo{http://lattes.cnpq.br/7764277601641080}                 % optional, remove / comment the line if not wanted
%\photo[64pt][0.4pt]{picture}                       % optional, remove / comment the line if not wanted; '64pt' is the height the picture must be resized to, 0.4pt is the thickness of the frame around it (put it to 0pt for no frame) and 'picture' is the name of the picture file
% \quote{Some quote}                                 % optional, remove / comment the line if not wanted

% to show numerical labels in the bibliography (default is to show no labels); only useful if you make citations in your resume
%\makeatletter
%\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
%\makeatother
%\renewcommand*{\bibliographyitemlabel}{[\arabic{enumiv}]}% CONSIDER REPLACING THE ABOVE BY THIS

% bibliography with mutiple entries
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%\begin{CJK*}{UTF8}{gbsn}                          % to typeset your resume in Chinese using CJK
%-----       resume       ---------------------------------------------------------
\makecvtitle

\section{Educación}
\cventry{2015--Interrumpida}{Posgrado en Ingeniería de Transportes y Gestión territorial}{Universidade Federal de Santa Catarina}{Florianópolis/Brasil}{\textit{Maestría}}{Las disciplinas abordaron una amplia linea de investigación y métodos para solucionar problemas de transportes.}  % arguments 3 to 6 can be left empty
\cventry{2004--2005}{Especialización en Sistemas de Información con énfasis en Tecnología de la Información}{Faculdade Eniac}{Guarulhos/Brasil}{\textit{Lato Sensu}}{Las disciplinas abordaron diversas tecnologías de información y comunicación. En la conclusión de la especialización fue entregada y defendida una monografía sobre La importancia del uso de software libre en telecentros comunitarios.}

\cventry{2003--2004}{Tecnología en Base de datos}{Faculdade Eniac}{Guarulhos/Brasil}{\textit{Pre-grado}}{Las clases ministradas tuvieron como enfoque el dominio de los conceptos sobre sistemas de base de datos, modelado de bases de datos y optimización}


\section{Experiencia}
\subsection{Laboral}
\cventry{2016--}{Cientista de datos y desarrollador de sistemas}{Independiente/Autónomo}{}{}{Análisis y visualización de datos; Análisis de  literaturas científicas para resolución de problemas; Análisis de librerías, de sus funcionalidades y desempeño; Desarrollo de aplicaciones web para visualización de los datos; Utilización de conceptos de Ciencia Abierta; etc. \newline{}%
Participación en los proyectos:%
\begin{itemize}%
\item Sistema de análisis de características visco-elásticas de pavimentos en ensayo en laboratorio;
\item Tablero de visualización de incidencia y estimación de influenza en Brasil;
\item Tablero de visualización de casos de dengue (estados brasileños participantes);
\end{itemize}}

\cventry{2013--2016}{Analista de Sistemas}{Fundação de Amparo a Pesquisa e Extensão Universitária (FAPEU)}{Florianópolis/Brasil}{}{Análise de literaturas internacionais para investigar métodos de apoio para sistemas de transportes, como: pesagem em movimento em alta velocidade e ensaios de fadiga e módulo complexo; Desenvolvimento de sistemas e testes dos métodos analisados; Atividades desenvolvidas utilizando Processamento de sinais digitais, Inteligencia Artificial.}

\cventry{2011--2013}{Analista Programador de Sistemas}{Cetil Sistemas de Informática S/A, CETIL}{Florianópolis/Brasil}{}{Análise e desenvolvimento de sistemas destinados à administração pública, como gestão de: trâmites de documentos e processos, texto legal, trâmites do legislativo, ocorrências e portal de transparência. Utilização das tecnologias: .NET, VB, SQL Server, Kettle. Atuação como contador e revisor de contagens em Ponto de Função.}

\cventry{2011--2011}{Analista de Sistemas}{Victory Consulting (VICTORY)}{São Paulo/Brasil}{}{Desenvolvimento de ferramentas de apoio para gestão de benefícios de plano de saúde e qualidade de vida. Utilização das tecnologias: PHP, JS, jQuery, DotProject, MySQL, Eclipse, Evolus Pencil, PHP Unit, Yii Framework, etc.}

\cventry{2010--2010}{Representante Internacional}{ECELA Spanish Language Schools (ECELA)}{Santiago/Chile}{}{Vendas de curso de imersão em espanhol para escolas no Chile, Argentina e Perú, tradução de materiais promocionais de/para português, inglês e espanhol; e desenvolvimento de sítios Web.}

\cventry{2007--2009}{Analista de Tecnologia da Informação}{Prefeitura Municipal de Guarulhos (PMG)}{Guarulhos/Brasil}{}{Levantamento, análise e desenvolvimento de sistemas de apoio à gestão pública como gerenciadores de trâmites de documentos e processos, gestão de contas públicas e sistemas de apoio a secretaria de educação e assistência social.}

\cventry{2006--2007}{Profesor}{Centro de Assistência e Promoção Social Nosso Lar (NOSSO LAR)}{Guarulhos/Brasil}{}{Professor de Curso Técnico em Informática. Aulas ministradas de Banco de Dados, Linguagem de Programação WEB e WEB Design.}

\cventry{2006--2007}{Desenvolvedor de Sistemas}{Uacari Consultoria de Informática UACARI}{Guarulhos/Brasil}{}{Desenvolvimento e manutenção de sistemas e sites, utilizando tecnologias como Java, PHP, MySQL, SQL Server, Flash, JavaScript. Instalação e configuração de estação de trabalho com sistemas operacionais livres GNU/Linux. Administração de rede de ambiente de desenvolvimento. Acompanhamento de atividades de instalação e configuração de servidores GNU/Linux. Atividades comerciais e administrativas como criação de propostas comerciais, visitação de clientes, definição de modelo de negócio, etc.}

\cventry{2005--2005}{Instructor}{Colégio e Faculdade ENIAC (ENIAC)}{Guarulhos/Brasil}{}{Professor substituto de disciplinas como banco de dados, e-commerce e programação WEB dos cursos de Bacharelado em Sistemas de Informação e Tecnologia em Banco de Dados e Tecnologia em Desenvolvimento WEB. Professor suplente e professor de aulas práticas do curso técnico em informática.}

\cventry{2005--2005}{Analista de Sistemas Jr}{Vemac Comércio e Serviços LTDA - ME (VEMAC)}{São Paulo/Brasil}{}{Análise e desenvolvimento de sistema computacional de apoio às unidades básicas de saúde.}

\cventry{2002--2004}{Técnico em Informática}{Colégio Eniac (ENIAC)}{Guarulhos/Brasil}{}{Desenvolvimento de sistemas e sites de apoio à gestão escolar.}

\cventry{2002--2002}{Técnico em Informática}{QualityWay (QUALITY WAY)}{São Paulo/Brasil}{}{A função desempenhada foi dedicada ao desenvolvimento de um sistema interno para gestão de recursos e de projetos de auditoria de processos de qualidade.}

\cventry{1999--1999}{Monitor de aulas de informática}{Instituto Data Brasil de Educação Profissional (DATABRASIL)}{Guarulhos/Brasil}{}{Monitor de aulas de informática básica e avançada e monitor de laboratório.}

\subsection{Proyectos personales}
\cventry{2015--}{Open Science and Weigh in Motion Research(OpenWIM)}{Independent Researcher}{}{}{The proposal of the OpenWIM Project is to create an open environment to support WIM researchers to improve their research using open science concepts.}

\section{Languages}
\cvitemwithcomment{Portugués}{Nativo}{}
\cvitemwithcomment{Español}{Fluente}{}
\cvitemwithcomment{Inglés}{Intermedio}{Buena lectura, buena comprensión auditiva, escritura técnica}
\cvitemwithcomment{Italiano}{Intermedio}{Buena lectura, buena comprensión auditiva}

%\section{Computer skills}
%\cvdoubleitem{category 1}{XXX, YYY, ZZZ}{category 4}{XXX, YYY, ZZZ}
%\cvdoubleitem{category 2}{XXX, YYY, ZZZ}{category 5}{XXX, YYY, ZZZ}
%\cvdoubleitem{category 3}{XXX, YYY, ZZZ}{category 6}{XXX, YYY, ZZZ}

%\section{Interests}
%\cvitem{hobby 1}{Description}
%\cvitem{hobby 2}{Description}
%\cvitem{hobby 3}{Description}

\section{Cursos extras}
\cvlistitem{Intro to Hadoop and MapReduce. Udacity (2016)}
\cvlistitem{Intro to Data Science. Udacity (2014)}
\cvlistitem{Machine Learning: Supervised Learning. Udacity (2014)}
\cvlistitem{Intro to Descriptive Statistics. Udacity (2014)}
\cvlistitem{Design of Computer Programs. Udacity (2012)}

%\section{Extra 2}
%\cvlistdoubleitem{Item 1}{Item 4}
%\cvlistdoubleitem{Item 2}{Item 5\cite{book1}}
%\cvlistdoubleitem{Item 3}{Item 6. Like item 3 in the single column list before, this item is particularly long to wrap over several lines.}

%\section{References}
%\begin{cvcolumns}
%  \cvcolumn{Category 1}{\begin{itemize}\item Person 1\item Person 2\item Person 3\end{itemize}}
%  \cvcolumn{Category 2}{Amongst others:\begin{itemize}\item Person 1, and\item Person 2\end{itemize}(more upon request)}
%  \cvcolumn[0.5]{All the rest \& some more}{\textit{That} person, and \textbf{those} also (all available upon request).}
%\end{cvcolumns}

% Publications from a BibTeX file without multibib
%  for numerical labels: \renewcommand{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}% CONSIDER MERGING WITH PREAMBLE PART
%  to redefine the heading string ("Publications"): \renewcommand{\refname}{Articles}
\nocite{*}
\bibliographystyle{plain}
\bibliography{publications}                        % 'publications' is the name of a BibTeX file

% Publications from a BibTeX file using the multibib package
%\section{Publications}
%\nocitebook{book1,book2}
%\bibliographystylebook{plain}
%\bibliographybook{publications}                   % 'publications' is the name of a BibTeX file
%\nocitemisc{misc1,misc2,misc3}
%\bibliographystylemisc{plain}
%\bibliographymisc{publications}                   % 'publications' is the name of a BibTeX file

\end{document}


%% end of file `template.tex'.
